---
title: "0_Simulation"
author: "Arturo Bertero"
date: "2025-02-28"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r}
library(pacman)
p_load(tidyverse, ggplot2, igraph, ggraph)
```

# Introduction

In this document I simulate PTV data to see how these scores translates into: 

- Individual level belief system, and their mean constraint
- PTV gap: measure of partisanship proposed by [this paper](https://www.sciencedirect.com/science/article/abs/pii/S026137941830533X). It is the delta betweeen max and min PTV. 
- AP of Wagner: to simulate data, I use [its example](https://www.sciencedirect.com/science/article/abs/pii/S0261379420300822?via%3Dihub). In the paper u see the formula. AP is basically the average affective distance of other parties from one’s most liked party. 

# Simulation

Suppose in a country we have four parties, and 10 individuals rating them. 

```{r}
# Create example data
df <- tibble::tibble(
  Voter = c(1, 2, 3, 4, 5, 6, 7, 8), 
  PTV_A = c(10, 10, 10, 5, 10, 4, 10, 0),
  PTV_B = c(0, 0, 5, 0, 5, 4, 10, 0),
  PTV_C = c(0, 0, 0, 0, 5, 3, 10, 0),
  PTV_D = c(0, 9, 5, 0, 5, 3, 10, 0)) 
```


## PTV measures

We start from the easiest measure. We compute the PTV gap, on all datasets. 

```{r}
# Compute PTV Gap (Max - Second Max)
df <- df %>%
  rowwise() %>%
  mutate(
    PTV_Gap = {
      sorted_scores <- sort(c_across(PTV_A:PTV_D), decreasing = TRUE)
      ifelse(length(sorted_scores) >= 2, sorted_scores[1] - sorted_scores[2], NA)
    }
  ) %>%
  ungroup()
```

Now AP, unweighted

```{r}
# Compute Affective Polarization using Wagner's Formula
df <- df %>%
  rowwise() %>%
  mutate(
    like_max = max(c_across(PTV_A:PTV_D), na.rm = TRUE),  # Identify the most liked party
    n_p = sum(!is.na(c_across(PTV_A:PTV_D))) - 1,  # Count the number of other parties
    AP = ifelse(n_p > 0, sqrt(sum((c_across(PTV_A:PTV_D) - like_max)^2, na.rm = TRUE) / n_p), NA)
  ) %>%
  ungroup() %>%
  select(-like_max, -n_p)  # Drop intermediate variables
```

Finally, we compute PTV_SD.

```{r}
# Compute PTV_SD (Standard Deviation of PTV Scores)
df <- df %>%
  rowwise() %>%
  mutate(
    PTV_SD = ifelse(sum(!is.na(c_across(PTV_A:PTV_D))) > 1, 
                    sd(c_across(PTV_A:PTV_D), na.rm = TRUE), NA_real_)
  ) %>%
  ungroup()

# Ensure numeric format
df <- df %>%
  mutate(PTV_SD = as.numeric(PTV_SD))

```

Let's visualize a comparison of the measures. 
```{r}
df = round(df, digits = 3)

df
```


# Old

```{r}
# Function to compute absolute difference matrix 
compute_difference_matrix <- function(ptv_row) {
  ptv_values <- as.numeric(ptv_row)  
  party_labels <- names(ptv_row)  
  
  # Ensure at least two valid PTV values exist
  if (length(ptv_values) < 2) {
    return(NULL)  
  }
  
  # Generate all pairwise combinations of PTV variables
  pairwise_combinations <- expand.grid(Party = party_labels, Compared_Party = party_labels, stringsAsFactors = FALSE)
  
  # Compute absolute differences for each pair
  pairwise_combinations$Difference <- abs(ptv_values[match(pairwise_combinations$Party, party_labels)] -
                                          ptv_values[match(pairwise_combinations$Compared_Party, party_labels)])
  
  return(pairwise_combinations)
}

# Apply function to df
df_matrices_list <- map(1:nrow(df), function(i) {
  compute_difference_matrix(df[i, 2:5])  
})

# Name each element 
names(df_matrices_list) <- df$Voter
```


And I visualize the 10 belief systems. 

```{r}
# Function to plot PTV belief system 
plot_ptv_network <- function(matrix_data, voter_id) {
  if (is.null(matrix_data) || nrow(matrix_data) == 0) {
    message(paste("Voter", voter_id, ": No valid PTV differences to plot."))
    return(NULL)
  }
  
  # Convert to igraph 
  g <- graph_from_data_frame(matrix_data, directed = FALSE)
  
  # Set edge weights
  E(g)$weight <- matrix_data$Difference
  
  # Plot network using ggraph
  ggraph(g, layout = "circle") +
    geom_edge_link(aes(width = weight), color = "blue", alpha = 0.7) +
    geom_node_point(size = 5, color = "red") +
    geom_node_text(aes(label = name), repel = TRUE, size = 5) +
    scale_edge_width(range = c(0.5, 5)) +  # Scale edge weights
    theme_void() +
    labs(title = paste("PTV Belief System - Voter", voter_id))
}

# Loop for fitting to all voters
for (i in seq_along(df_matrices_list)) {
  print(plot_ptv_network(df_matrices_list[[i]], names(df_matrices_list)[i]))
}

```
