---
title: "Robustness checks"
author: "Arturo Bertero"
date: "2024-04-15"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library("pacman")
p_load(tidyverse, here, haven, countrycode, vdemdata, psych, lavaan, ltm, magick,
       janitor, conflicted, sjPlot, BMA, BMS, fastDummies, ggplot2, reshape2, ggeffects,
       hrbrthemes, viridis, ggrepel, jtools, patchwork, kableExtra, bootnet, qgraph, webshot)

#conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
```

```{r}
# import final data
data = read_rds(here("Input", "final_data", "final.rds"))

#as factor
data$country = as.factor(data$country)
data$year = as.factor(data$year)
data$country_year = as.factor(data$country_year)
```


# Introduction
Document showing graphs for Supplment and Article. I begin with original variables.

# Descriptives

## Table_1 (Article)
```{r}
#data from "2_EES_Models.Rmd"
Original_n = c(11678,13063,13549,28861,27069,30064,26538,150822)
Losses = c(16.47,19.27,16.00,32.66,14.34,24.00,6.53,19.14)
Year = c(1989,1994,1999,2004,2009,2014,2019,"Total")
n = c(9755,10546,11381,19435,23186,22850,24806,121959)

#Table_1 
Table_1 = data_frame(Year, Original_n, n, Losses)

sjPlot::tab_df(Table_1, file = here("Output", "Article", "Table_1.doc"))
```


```{r}
# data preparation
violin_data = data %>% 
  select("EES_COR_constraint", "EES_GGM_huge_constraint", "EES_GGM_glasso_constraint") 

long_violin_data = melt(violin_data, variable.name = "Model", value.name = "Value")

# violin plot

# Calculate the sample sizes
sample_size <- long_violin_data %>% group_by(Model) %>% summarize(num=n())

# Join the sample and violin data 
plot_data <- long_violin_data %>%
  left_join(sample_size, by = "Model") %>%
  mutate(myaxis = paste0(Model, "\n", "n=", num))

# Create the plot
violin_plot <- ggplot(plot_data, aes(x=myaxis, y=Value, fill=Model)) +
  geom_violin(position=position_dodge(width=0.25), width=0.8) +
  geom_boxplot(width=0.1, color="grey", alpha=0.2, position=position_dodge(width=0.25)) +
  scale_fill_viridis(discrete = TRUE) +
  theme_ipsum(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=14)
  ) +
  labs(title="Aggregated distribution of Constraint", x="", y="Constraint") +
  scale_x_discrete(labels=c("Correlation", "Glasso", "Huge"))

```

```{r}
# data preparation
violin_data_aspl = data %>% 
  select("EES_COR_aspl", "EES_GGM_huge_aspl", "EES_GGM_glasso_aspl") 

long_violin_data_aspl = melt(violin_data_aspl, variable.name = "Model", value.name = "Value")

# violin plot

# Calculate the sample sizes
sample_size <- long_violin_data_aspl %>% group_by(Model) %>% summarize(num=n())

# Join the sample and violin data 
plot_data_aspl <- long_violin_data_aspl %>%
  left_join(sample_size, by = "Model") %>%
  mutate(myaxis = paste0(Model, "\n", "n=", num))

# Create the plot
violin_plot_aspl <- ggplot(plot_data_aspl, aes(x=myaxis, y=Value, fill=Model)) +
  geom_violin(position=position_dodge(width=0.25), width=0.8) +
  geom_boxplot(width=0.1, color="grey", alpha=0.2, position=position_dodge(width=0.25)) +
  scale_fill_viridis(discrete = TRUE) +
  theme_ipsum(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=14)
  ) +
  labs(title="Aggregated distribution of ASPL", x="", y="ASPL") +
  scale_x_discrete(labels=c("Correlation", "Glasso", "Huge"))

```

## Fig_1 (Supplement)
Aggregated frequency distribution with outliers and original scales. 

```{r}
#print desc_1
Fig_1 = violin_plot + violin_plot_aspl 
print(Fig_1)

#save
ggsave(here("Output", "Supplement", "Fig_1.jpg"), Fig_1, width = 16, height = 9, dpi = 600)
```

## Fig_1_bis (Supplement)
Remove outliers and re-do figure 1

```{r}
#robustness: remove outliers from aspl

# filter outliers
num_sd <- 3

# cor
# Calculate mean and sd
mean_aspl <- mean(data$EES_COR_aspl, na.rm = TRUE)
sd_aspl <- sd(data$EES_COR_aspl, na.rm = TRUE)

# Filter out outliers
data <- data %>%
  filter(EES_COR_aspl > (mean_aspl - num_sd * sd_aspl) & EES_COR_aspl < (mean_aspl + num_sd * sd_aspl))

# glasso
# Calculate mean and sd
mean_aspl <- mean(data$EES_GGM_glasso_aspl, na.rm = TRUE)
sd_aspl <- sd(data$EES_GGM_glasso_aspl, na.rm = TRUE)

# Filter out outliers
data <- data %>%
  filter(EES_GGM_glasso_aspl > (mean_aspl - num_sd * sd_aspl) & EES_GGM_glasso_aspl < (mean_aspl + num_sd * sd_aspl))

# huge
# Calculate mean and sd
mean_aspl <- mean(data$EES_GGM_huge_aspl, na.rm = TRUE)
sd_aspl <- sd(data$EES_GGM_huge_aspl, na.rm = TRUE)

# Filter out outliers
data <- data %>%
  filter(EES_GGM_huge_aspl > (mean_aspl - num_sd * sd_aspl) & EES_GGM_huge_aspl < (mean_aspl + num_sd * sd_aspl))

```

```{r}
# data preparation
violin_data = data %>% 
  select("EES_COR_constraint", "EES_GGM_huge_constraint", "EES_GGM_glasso_constraint") 

long_violin_data = melt(violin_data, variable.name = "Model", value.name = "Value")

# violin plot

# Calculate the sample sizes
sample_size <- long_violin_data %>% group_by(Model) %>% summarize(num=n())

# Join the sample and violin data 
plot_data <- long_violin_data %>%
  left_join(sample_size, by = "Model") %>%
  mutate(myaxis = paste0(Model, "\n", "n=", num))

# Create the plot
violin_plot <- ggplot(plot_data, aes(x=myaxis, y=Value, fill=Model)) +
  geom_violin(position=position_dodge(width=0.25), width=0.8) +
  geom_boxplot(width=0.1, color="grey", alpha=0.2, position=position_dodge(width=0.25)) +
  scale_fill_viridis(discrete = TRUE) +
  theme_ipsum(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=14)
  ) +
  labs(title="Aggregated distribution of Constraint", x="", y="Constraint") +
  scale_x_discrete(labels=c("Correlation", "Glasso", "Huge"))

```

```{r}
# data preparation
violin_data_aspl = data %>% 
  select("EES_COR_aspl", "EES_GGM_huge_aspl", "EES_GGM_glasso_aspl") 

long_violin_data_aspl = melt(violin_data_aspl, variable.name = "Model", value.name = "Value")

# violin plot

# Calculate the sample sizes
sample_size <- long_violin_data_aspl %>% group_by(Model) %>% summarize(num=n())

# Join the sample and violin data 
plot_data_aspl <- long_violin_data_aspl %>%
  left_join(sample_size, by = "Model") %>%
  mutate(myaxis = paste0(Model, "\n", "n=", num))

# Create the plot
violin_plot_aspl <- ggplot(plot_data_aspl, aes(x=myaxis, y=Value, fill=Model)) +
  geom_violin(position=position_dodge(width=0.25), width=0.8) +
  geom_boxplot(width=0.1, color="grey", alpha=0.2, position=position_dodge(width=0.25)) +
  scale_fill_viridis(discrete = TRUE) +
  theme_ipsum(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=14)
  ) +
  labs(title="Aggregated distribution of ASPL", x="", y="ASPL") +
  scale_x_discrete(labels=c("Correlation", "Glasso", "Huge"))

```

```{r}
#print desc_1
Fig_1 = violin_plot + violin_plot_aspl 
print(Fig_1)

#save
ggsave(here("Output", "Supplement", "Fig_1_bis.jpg"), Fig_1, width = 16, height = 9, dpi = 600)
```

## Fig_2 constraint over time (Supplement)

```{r fig.width=16, fig.height=8}
# data
cons_trend <- data %>%
  select(year, country, EES_COR_constraint, EES_GGM_huge_constraint, EES_GGM_glasso_constraint) 

long_cons_trend = melt(cons_trend, variable.name = "Model", value.name = "Value")


# Plot
Fig_2 = long_cons_trend %>%
  ggplot(aes(x = year, y = Value, group = interaction(country, Model), color = Model)) +
  geom_line() +
  geom_point() +
  facet_wrap(~country) +  
  scale_color_viridis_d(labels = c("Correlation", "Glasso", "Huge")) +  
  theme_ipsum() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(hjust = 0.5)) +
  labs(
    title = "Temporal Development of Constraint",
    x = "Year", 
    y = "Constraint",
    color = "Model Type"
  )

# Print the graph
print(Fig_2)

#save
ggsave(here("Output", "Supplement", "Fig_2.jpg"), Fig_2, width = 16, height = 9, dpi = 600)
```

## Fig_3 ASPL over time (Supplment)

```{r fig.width=16, fig.height=8}
# data
aspl_trend <- data %>%
  select(year, country, EES_COR_aspl, EES_GGM_huge_aspl, EES_GGM_glasso_aspl) 

long_aspl_trend = melt(aspl_trend, variable.name = "Model", value.name = "Value")


#graph
Fig_3 = long_aspl_trend %>%
  ggplot(aes(x = year, y = Value, group = interaction(country, Model), color = Model)) +
    geom_line() +
    geom_point() +
    facet_wrap(~country) +  
    scale_color_viridis_d(labels = c("Correlation", "Glasso", "Huge")) + 
    theme_ipsum() +
    theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(hjust = 0.5)) +
    labs(title = "Temporal Development of ASPL",
         x = "Year", 
         y = "ASPL",
         color = "Model Type") 

# Print the graph
print(Fig_3)

#save
ggsave(here("Output", "Supplement", "Fig_3.jpg"), Fig_3, width = 16, height = 9, dpi = 600)
```
## Fig_4 scatterplot ASPL constraint (Supplement)
Scatterplot constraint and ASPL to show networks scoring differently on the two measures

```{r}
#data_scatt
data_scatt <- data %>%
  mutate(
    iso2c = countrycode(substr(country_year, 1, 3), "iso3c", "iso2c"),
    year = substr(country_year, 7, 8),
    country_year_modified = paste(iso2c, year, sep = "_")
  )

# Identify extreme points
extreme_points <- data_scatt %>%
  filter(
    EES_GGM_huge_constraint == max(EES_GGM_huge_constraint) | 
    EES_GGM_huge_constraint == min(EES_GGM_huge_constraint) |
    EES_GGM_huge_aspl == max(EES_GGM_huge_aspl) | 
    EES_GGM_huge_aspl == min(EES_GGM_huge_aspl))

#Plot with labels
Fig_4 = ggplot(data_scatt, aes(x = EES_GGM_huge_constraint, y = EES_GGM_huge_aspl)) +
  geom_point(size = 1) +  
  geom_smooth(method = lm, color = "pink", fill = "#69b3a2", se = TRUE) +
  theme_ipsum(base_size = 14) +
  labs(
    x = "Constraint",
    y = "ASPL"
  ) +
  geom_label_repel(
    data = extreme_points, 
    aes(label = country_year_modified), 
    size = 3,  
    box.padding = 0.3,  
    point.padding = 0.5,  
    label.size = 0.25,  
    fill = 'white',  
    color = 'black' 
  ) +
  theme_ipsum() +
  theme(
    axis.title.x = element_text(size = 14),  
    axis.title.y = element_text(size = 14)  
  )

print(Fig_4)

#save
ggsave(here("Output", "Supplement", "Fig_4.jpg"), Fig_4, width = 16, height = 9, dpi = 600)
```
## Fig_5 (Supplement)
Visualize extreme cases

```{r}
# import network data to show examples
EES_data = read_rds(here("Input", "data", "EES.rds"))

#Network models
prt_94_fit = estimateNetwork(EES_data[["1994"]][["PRT"]], default = "huge", tuning = 0.15)
lux_99_fit = estimateNetwork(EES_data[["1999"]][["LUX"]], default = "huge", tuning = 0.15)
mlt_14_fit = estimateNetwork(EES_data[["2014"]][["MLT"]], default = "huge", tuning = 0.15)
rou_19_fit = estimateNetwork(EES_data[["2019"]][["ROU"]], default = "huge", tuning = 0.15)

#Network matrices for highlighted cases
prt_94 = prt_94_fit$graph
lux_99 = lux_99_fit$graph
mlt_14 = mlt_14_fit$graph
rou_19 = rou_19_fit$graph

#prt_94
shortnames_prt_94 = c("CDU", "PS", "PSD", "CDS-PP", "PSN")
longnames_prt_94 = c("Democratic Unity Coalition", "Socialist Party", "Social Democratic Party", "People's Party", "National Solidarity Party")

prt_94_graph<-qgraph(prt_94, 
  layout = "spring", theme = "Borkulo", GLratio = 2,
  labels = shortnames_prt_94, nodeNames = longnames_prt_94,
  label.scale=FALSE, label.cex = 1, borders = F,
  legend.cex = 0.45, legend = TRUE, details = FALSE, vsize=7.0,
 title = "Portugal 1994", color = "#69b3a2",
 filetype="jpg", filename=here("Output", "Supplement", "Fig_5", "1"))

#lux_99
shortnames_lux_99 = c("DG", "GAL", "DL", "LSAP", "DP", "CSV", "ADR")
longnames_lux_99 = c("The Greens","Green and Liberal Alliance", "The Left", "Luxembourg Socialist Workers' Party", "Democratic Party",
  "Christian Social People's Party", "Alternative Democratic Reform Party")

lux_99_graph<-qgraph(lux_99, GLratio = 2, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames_lux_99, nodeNames = longnames_lux_99,
  label.scale=FALSE, label.cex = 1, borders = F,
  legend.cex = 0.45, legend = TRUE, details = FALSE, vsize=7.0,
 title = "Luxembourg 1999", color = "#69b3a2",
 filetype="jpg", filename=here("Output", "Supplement", "Fig_5", "2"))

#mlt_14
shortnames_mlt_14 = c("LP", "NP", "DA")
longnames_mlt_14 = c("Labour Party", "Nationalist Party", "Democratic Alternative")

mlt_14_graph<-qgraph(mlt_14, 
  layout = "spring", theme = "Borkulo", GLratio = 2,
  labels = shortnames_mlt_14, nodeNames = longnames_mlt_14,
  label.scale=FALSE, label.cex = 1, borders = F,
  legend.cex = 0.45, legend = TRUE, details = FALSE, vsize=7.0,
 title = "Malta 2014", color = "#69b3a2",
 filetype="jpg", filename=here("Output", "Supplement", "Fig_5", "3"))

#rou_19
shortnames_rou_19 = c("PSD", "USR", "ALDE", "PPR", "PNL", "UDMR", "PMP", "PLUS+", "A" )
longnames_rou_19 = c("Social Democratic Party", "Save Romania Union", "Alliance of Liberals and Democrats", "PRO Romania", "National Liberal Party", "Hungarian Democratic Alliance of Romania", "People's Movement Party", "Freedom, Unity and Solidarity Party", "Alliance 2020")

rou_19_graph<-qgraph(rou_19, 
  layout = "spring", theme = "Borkulo", GLratio = 2, 
  labels = shortnames_rou_19, nodeNames = longnames_rou_19,
  label.scale=FALSE, label.cex = 1, borders = F,
  legend.cex = 0.45, legend = TRUE, details = FALSE, vsize=7.0,
 title = "Romania 2019", color = "#69b3a2",
 filetype="jpg", filename=here("Output", "Supplement", "Fig_5", "4"))

```


# Part 1: What does predict network characteristics? 

## ASPL/constraint

### Data managment for regressions 

```{r}
# np_w as absoulte value
data$EES_COR_np_w = abs(data$EES_COR_np_w)
data$EES_GGM_glasso_np_w = abs(data$EES_GGM_glasso_np_w)
data$EES_GGM_huge_np_w = abs(data$EES_GGM_huge_np_w)
```

```{r}
# rescale function
rescale01 <- function(x) {(x - min(x)) / (max(x) - min(x))}

# Manually applying the function
data$EES_GGM_glasso_aspl = rescale01(data$EES_GGM_glasso_aspl) 
data$EES_GGM_glasso_np_i = rescale01(data$EES_GGM_glasso_np_i) 
data$EES_GGM_glasso_np_w = rescale01(data$EES_GGM_glasso_np_w)
data$EES_GGM_huge_aspl = rescale01(data$EES_GGM_huge_aspl) 
data$EES_GGM_huge_np_i = rescale01(data$EES_GGM_huge_np_i) 
data$EES_GGM_huge_np_w = rescale01(data$EES_GGM_huge_np_w)
data$EES_COR_aspl = rescale01(data$EES_COR_aspl) 
data$EES_COR_np_i = rescale01(data$EES_COR_np_i) 
data$EES_COR_np_w = rescale01(data$EES_COR_np_w)
data$educ = rescale01(data$educ)
data$ideol = rescale01(data$ideol)
data$mass_mob = rescale01(data$mass_mob)
data$p_inst_k = rescale01(data$p_inst_k)
data$p_inst = rescale01(data$p_inst)
data$pint = rescale01(data$pint)
data$pola = rescale01(data$pola)
data$turnout = rescale01(data$turnout)
data$ENEP = rescale01(data$ENEP)
data$gallagher = rescale01(data$gallagher)
data$ihdi = rescale01(data$ihdi)
```

### Model 1-7 (Article and Supplement)
-M1: huge_aspl = p_inst + pola + pint + country + year
-M2: huge_aspl = p_inst + pola + pint + country + year + ENEP + gallagher + ihdi

Article:

```{r}
M1 <- lm(EES_GGM_huge_aspl ~ p_inst + pola + pint + country + year , data = data)
M2 <- lm(EES_GGM_huge_aspl ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

tab_model(
  list(M1, M2),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M1 (F.E.)", "M2 (Controls)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS models on ASPL of PTV networks",
  string.pred = " ",
  auto.label = FALSE,
  terms = c("p_inst", "pola", "pint"),
  pred.labels = c("Party institutionalization", "Political polarization", "Political interest"),
  file = here("Output", "Article", "Table_2.html")
)

#save as doc
tab_model(
  list(M1, M2),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M1 (F.E.)", "M2 (Controls)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS models on ASPL of PTV networks",
  string.pred = " ",
  auto.label = FALSE,
  terms = c("p_inst", "pola", "pint"),
  pred.labels = c("Party institutionalization", "Political polarization", "Political interest"),
  file = here("Output", "Article", "Table_2.doc")
)
```


Supplement: full models, considering other networks (huge, glasso, cor)

```{r}
M2 <- lm(EES_GGM_huge_aspl ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

M3 <- lm(EES_GGM_glasso_aspl ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

M4 <- lm(EES_COR_aspl ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

tab_model(
  list(M2, M3, M4),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M2 (huge ASPL)", "M3 (glsso ASPL)", "M4 (correlation ASPL)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS fixed effects (country and years) on ASPL of PTV networks",
  string.pred = " ",
  auto.label = T,
  file = here("Output", "Supplement", "Tab_1.html")
)
```


Supplement: full models on constraint (huge, glasso, cor)

```{r}
M5 <- lm(EES_GGM_huge_constraint ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

M6 <- lm(EES_GGM_glasso_constraint ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

M7 <- lm(EES_COR_constraint ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

tab_model(
  list(M5, M6, M7),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M5 (huge constraint)", "M6 (glasso constraint)", "M7 (correlation constraint)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS fixed effects (country and years) on constraint of PTV networks",
  string.pred = " ",
  auto.label = T,
  file = here("Output", "Supplement", "Tab_2.html")
)
```

## Negative/positive raito

### Data mang for regression

```{r}
#import cses data (cleaned)
aff_pola = read_rds(here("Input", "final_data", "IV", "aff_pola_long.rds"))

#Merge with data
cses_cases <- aff_pola %>%
  inner_join(data, by = "country_year") %>% 
  rename(country = country.x,
         year = year.x)

#factor
cses_cases$year = as.factor(cses_cases$year)
cses_cases$country = as.factor(cses_cases$country)

# Modified rescale function to handle NA values
rescale01 <- function(x) {
  min_x <- min(x, na.rm = TRUE)
  max_x <- max(x, na.rm = TRUE)
  (x - min_x) / (max_x - min_x)
}

# Apply the rescale function to new columns, preserving NA values
cses_cases$PAP_partisans <- rescale01(cses_cases$PAP_partisans)
cses_cases$PAP_electorate <- rescale01(cses_cases$PAP_electorate)
cses_cases$LAP_partisans <- rescale01(cses_cases$LAP_partisans)
cses_cases$LAP_electorate <- rescale01(cses_cases$LAP_electorate)
```

### Model 8-15

Article: M8 to M11, models for huge_np_w and _i

```{r}
M8 <- lm(EES_GGM_huge_np_w ~ p_inst + pola + pint + country + year, data = data)

M9 <- lm(EES_GGM_huge_np_w ~ p_inst + pola + pint + country + year +
           ENEP + gallagher + ihdi, data = data)

M10 <- lm(EES_GGM_huge_np_i ~ p_inst + pola + pint + country + year, data = data)

M11 <- lm(EES_GGM_huge_np_i ~ p_inst + pola + pint + country + year +
           ENEP + gallagher + ihdi, data = data)

tab_model(
  list(M8, M9, M10, M11),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M8 (Weighted, F.E.)", "M9 (Weighted, controls)",
                "M10 (Integer, F.E.)", "M11 (Integer, controls)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS models on negative/positive ratio measures of PTV networks",
  string.pred = " ",
  auto.label = FALSE,
  terms = c("p_inst", "pola", "pint"),
  pred.labels = c("Party institutionalization", "Political polarization", "Political interest"),
  file = here("Output", "Article", "Table_3.html")
)

#save as doc
tab_model(
  list(M8, M9, M10, M11),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M8 (Weighted, F.E.)", "M9 (Weighted, controls)",
                "M10 (Integer, F.E.)", "M11 (Integer, controls)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS models on negative/positive ratio measures of PTV networks",
  string.pred = " ",
  auto.label = FALSE,
  terms = c("p_inst", "pola", "pint"),
  pred.labels = c("Party institutionalization", "Political polarization", "Political interest"),
  file = here("Output", "Article", "Table_3.doc")
)
```

Supplement: M9 to M15, full models for np_w and np_i (M9 and M11 same as above)

```{r}
M9  <- lm(EES_GGM_huge_np_w ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)
M11 <- lm(EES_GGM_huge_np_i ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

M12 <- lm(EES_GGM_glasso_np_w ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)
M13 <- lm(EES_GGM_glasso_np_i ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

M14 <- lm(EES_COR_np_w ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)
M15 <- lm(EES_COR_np_i ~ p_inst + pola + pint + country + year + ENEP + gallagher + ihdi, data = data)

tab_model(
  list(M9, M11, M12, M13, M14, M15),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M9 (huge, weighted)", "M11 (huge, integer)", 
                "M12 (glasso, weighted)", "M13 (glasso, integer)",
                "M14 (correlation, weighted)", "M15 (correlation, integer)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS fixed effects (country and years) on ratio measures of PTV networks",
  string.pred = " ",
  auto.label = T,
  file = here("Output", "Supplement", "Tab_3.html")
)

```

### Model 16-23

Article: M16- M18 (aff pola, cses); 
```{r}
M16 <- lm(EES_GGM_huge_aspl ~ PAP_electorate  + country + year +
         ENEP + gallagher + ihdi + pint, data = cses_cases)
M17 <- lm(EES_GGM_huge_np_w ~ PAP_electorate  + country + year +
            ENEP + gallagher + ihdi + pint, data = cses_cases)
M18 <- lm(EES_GGM_huge_np_i ~ PAP_electorate  + country + year +
            ENEP + gallagher + ihdi + pint, data = cses_cases)

tab_model(
  list(M16, M17, M18),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M16 (ASPL)", "M17 (Weighted ratio)", "M18 (Integer ratio)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS fixed effects (country and years) on ASPL and ratio measures of PTV networks. CSES cases",
  string.pred = " ",
  auto.label = FALSE,
  terms = c("PAP_electorate", "pint"),
  pred.labels = c("Partisan Affective Polarization", "Political interest"),
  file = here("Output", "Article", "Table_3.html")
)

#doc
tab_model(
  list(M16, M17, M18),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M16 (ASPL)", "M17 (Weighted ratio)", "M18 (Integer ratio)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS fixed effects (country and years) on ASPL and ratio measures of PTV networks. CSES cases",
  string.pred = " ",
  auto.label = FALSE,
  terms = c("PAP_electorate", "pint"),
  pred.labels = c("Partisan Affective Polarization", "Political interest"),
  file = here("Output", "Article", "Table_3.doc")
)
```

Supplement: M16- M23 (aff pola, cses, glasso); M16, M17 and M18 same as above 
```{r}
M16 <- lm(EES_GGM_huge_aspl ~ PAP_electorate  + country + year +
         ENEP + gallagher + ihdi + pint, data = cses_cases)
M17 <- lm(EES_GGM_huge_np_w ~ PAP_electorate  + country + year +
            ENEP + gallagher + ihdi + pint, data = cses_cases)
M18 <- lm(EES_GGM_huge_np_i ~ PAP_electorate  + country + year +
            ENEP + gallagher + ihdi + pint, data = cses_cases)

M19 <- lm(EES_GGM_huge_aspl ~ PAP_partisans  + country + year +
         ENEP + gallagher + ihdi + pint, data = cses_cases)
M20 <- lm(EES_GGM_huge_np_w ~ PAP_partisans  + country + year +
            ENEP + gallagher + ihdi + pint, data = cses_cases)
M21 <- lm(EES_GGM_huge_np_i ~ PAP_partisans  + country + year +
            ENEP + gallagher + ihdi + pint, data = cses_cases)

M22 <- lm(EES_GGM_glasso_np_w ~ PAP_electorate  + country + year +
         ENEP + gallagher + ihdi + pint, data = cses_cases)
M23 <- lm(EES_COR_np_w ~ PAP_electorate  + country + year +
         ENEP + gallagher + ihdi + pint, data = cses_cases)

tab_model(
  list(M16, M17, M18, M19, M20, M21, M22, M23),
  show.p = TRUE,
  p.style = "stars",
  p.threshold = c(0.1, 0.05, 0.01),
  dv.labels = c("M16 (Huge, ASPL)", "M17 (Huge, weighted ratio)", "M18 (Huge, integer ratio)",
                "M19 (Huge, ASPL)", "M20 (Huge, weighted ratio)", "M21 (Huge, integer ratio)",
                "M22 (Glasso, weighted ratio)", "M23 (Correlation, weighted ratio)"),
  collapse.ci = TRUE,
  show.aic = TRUE,
  title = "OLS fixed effects (country and years) on ASPL and ratio measures of PTV networks. CSES cases",
  string.pred = " ",
  auto.label = T,
  file = here("Output", "Supplement", "Tab_4.html")
)

```


# Part 2: What are the consequences of network characteristics? 

There are not outliers for turnout to be removed; I take the absolute of the np_w measure; I remove outliers for the np_i measure (from 143 to 136 observation); I remove outliers for the np_w measure (from 136 to 126 observation). I show models where ratio measures of huge networks predict EU turnout (turnout) and national turnout (turnout_nat). 

```{r}
# import final data
turnout = read_rds(here("Input", "final_data", "final_turnout.rds"))

#as factor
turnout$country = as.factor(turnout$country)
turnout$year = as.factor(turnout$year)
turnout$country_year = as.factor(turnout$country_year)
turnout$infla = as.numeric(turnout$infla)
turnout$mand = as.factor(turnout$mand)
```

## Outliers

```{r}
#robustness: remove outliers from turnout (zero)

# filter outliers
num_sd <- 3

# cor
# Calculate mean and sd
mean_turn <- mean(turnout$turnout, na.rm = TRUE)
sd_turn <- sd(turnout$turnout, na.rm = TRUE)

# Filter out outliers
turnout <- turnout %>%
  filter(turnout > (mean_turn - num_sd * sd_turn) & turnout < (mean_turn + num_sd * sd_turn))

```

```{r}
#robustness: remove outliers from np_i (7)

# filter outliers
num_sd <- 3

# cor
# Calculate mean and sd
mean_np <- mean(turnout$EES_COR_np_i, na.rm = TRUE)
sd_np <- sd(turnout$EES_COR_np_i, na.rm = TRUE)

# Filter out outliers
turnout <- turnout %>%
  filter(EES_COR_np_i > (mean_np - num_sd * sd_np) & EES_COR_np_i < (mean_np + num_sd * sd_np))

# glasso
# Calculate mean and sd
mean_np <- mean(turnout$EES_GGM_glasso_np_i, na.rm = TRUE)
sd_np <- sd(turnout$EES_GGM_glasso_np_i, na.rm = TRUE)

# Filter out outliers
turnout <- turnout %>%
  filter(EES_GGM_glasso_np_i > (mean_np - num_sd * sd_np) & EES_GGM_glasso_np_i < (mean_np + num_sd * sd_np))

# huge
# Calculate mean and sd
mean_np <- mean(turnout$EES_GGM_huge_np_i, na.rm = TRUE)
sd_np <- sd(turnout$EES_GGM_huge_np_i, na.rm = TRUE)

# Filter out outliers
turnout <- turnout %>%
  filter(EES_GGM_huge_np_i > (mean_np - num_sd * sd_np) & EES_GGM_huge_np_i < (mean_np + num_sd * sd_np))

```

```{r}
#robustness: remove outliers from np_w (10)

# filter outliers
num_sd <- 3

# cor
# Calculate mean and sd
mean_np <- mean(turnout$EES_COR_np_w, na.rm = TRUE)
sd_np <- sd(turnout$EES_COR_np_w, na.rm = TRUE)

# Filter out outliers
turnout <- turnout %>%
  filter(EES_COR_np_w > (mean_np - num_sd * sd_np) & EES_COR_np_w < (mean_np + num_sd * sd_np))

# glasso
# Calculate mean and sd
mean_np <- mean(turnout$EES_GGM_glasso_np_w, na.rm = TRUE)
sd_np <- sd(turnout$EES_GGM_glasso_np_w, na.rm = TRUE)

# Filter out outliers
turnout <- turnout %>%
  filter(EES_GGM_glasso_np_w > (mean_np - num_sd * sd_np) & EES_GGM_glasso_np_w < (mean_np + num_sd * sd_np))

# huge
# Calculate mean and sd
mean_np <- mean(turnout$EES_GGM_huge_np_w, na.rm = TRUE)
sd_np <- sd(turnout$EES_GGM_huge_np_w, na.rm = TRUE)

# Filter out outliers
turnout <- turnout %>%
  filter(EES_GGM_huge_np_w > (mean_np - num_sd * sd_np) & EES_GGM_huge_np_w < (mean_np + num_sd * sd_np))
```

## Fig_6 (Supplement)

Here is the graph of the distributions of EU turnout and national turnout. 

```{r}
# Data preparation
violin_data_aspl = turnout %>% 
  select(turnout, turnout_nat)

# Reshape the data to long format
long_violin_data_aspl = melt(violin_data_aspl, variable.name = "Model", value.name = "Value")

# Calculate the sample sizes
sample_size <- long_violin_data_aspl %>% group_by(Model) %>% summarize(num = n())

# Join the sample and violin data
plot_data_aspl <- long_violin_data_aspl %>%
  left_join(sample_size, by = "Model") %>%
  mutate(myaxis = paste0(Model, "\n", "n=", num))

# Create the plot
violin_plot_turnout <- ggplot(plot_data_aspl, aes(x = myaxis, y = Value, fill = Model)) +
  geom_violin(position = position_dodge(width = 0.25), width = 0.8) +
  geom_boxplot(width = 0.1, color = "grey", alpha = 0.2, position = position_dodge(width = 0.25)) +
  scale_fill_viridis(discrete = TRUE) +
  theme_ipsum(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14)
  ) +
  labs(title = "Aggregated distribution of Turnout", x = "", y = "Turnout") +
  scale_x_discrete(labels = c("EU Turnout", "National Turnout"))

print(violin_plot_turnout)

#save
ggsave(here("Output", "Supplement", "Fig_6.jpg"), violin_plot_turnout, width = 16, height = 9, dpi = 600)
```

## Data managment for regressions

```{r}
# np_w as absoulte value
turnout$EES_COR_np_w = abs(turnout$EES_COR_np_w)
turnout$EES_GGM_glasso_np_w = abs(turnout$EES_GGM_glasso_np_w)
turnout$EES_GGM_huge_np_w = abs(turnout$EES_GGM_huge_np_w)
```

```{r}
# rescale function
rescale01 <- function(x) {(x - min(x)) / (max(x) - min(x))}

# Manually applying the function
turnout$EES_GGM_glasso_aspl = rescale01(turnout$EES_GGM_glasso_aspl) 
turnout$EES_GGM_glasso_np_i = rescale01(turnout$EES_GGM_glasso_np_i) 
turnout$EES_GGM_glasso_np_w = rescale01(turnout$EES_GGM_glasso_np_w)
turnout$EES_GGM_huge_aspl = rescale01(turnout$EES_GGM_huge_aspl) 
turnout$EES_GGM_huge_np_i = rescale01(turnout$EES_GGM_huge_np_i) 
turnout$EES_GGM_huge_np_w = rescale01(turnout$EES_GGM_huge_np_w)
turnout$EES_COR_aspl = rescale01(turnout$EES_COR_aspl) 
turnout$EES_COR_np_i = rescale01(turnout$EES_COR_np_i) 
turnout$EES_COR_np_w = rescale01(turnout$EES_COR_np_w)
turnout$educ = rescale01(turnout$educ)
turnout$ideol = rescale01(turnout$ideol)
turnout$mass_mob = rescale01(turnout$mass_mob)
turnout$p_inst_k = rescale01(turnout$p_inst_k)
turnout$p_inst = rescale01(turnout$p_inst)
turnout$pint = rescale01(turnout$pint)
turnout$pola = rescale01(turnout$pola)
turnout$ENEP = rescale01(turnout$ENEP)
turnout$gallagher = rescale01(turnout$gallagher)
turnout$ihdi = rescale01(turnout$ihdi)
turnout$turnout = rescale01(turnout$turnout)
turnout$turnout_nat = rescale01(turnout$turnout_nat)
```

## Models 24-35 (Supplement)
First set of models: EU and national turnout, weighted IV

```{r}
# reg turnout
M24 = lm(turnout ~ EES_GGM_huge_np_w + EES_GGM_huge_aspl + country + year + ihdi + 
           pola + ENEP, data = turnout)
M25 = lm(turnout ~ EES_GGM_glasso_np_w + EES_GGM_glasso_aspl + country + year + ihdi + 
           pola + ENEP, data = turnout)
M26 = lm(turnout ~ EES_COR_np_w + EES_COR_aspl + country + year + ihdi +  
           pola + ENEP, data = turnout)

M27 = lm(turnout_nat ~ EES_GGM_huge_np_w + EES_GGM_huge_aspl + country + year + ihdi + 
           pola + ENEP, data = turnout)
M28 = lm(turnout_nat ~ EES_GGM_glasso_np_w + EES_GGM_glasso_aspl + country + year + ihdi + 
           pola + ENEP, data = turnout)
M29 = lm(turnout_nat ~ EES_COR_np_w + EES_COR_aspl + country + year + ihdi + 
           pola + ENEP, data = turnout)

tab_model(list(M24, M25, M26, M27, M28, M29),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M24 (EU turnout)", "M25 (EU turnout)", 
                        "M26 (EU turnout)", "M27 (National turnout,)",
                        "M28 (National turnout)", "M29 (National turnout)"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "OLS fixed effects (country and years) on EU and National turnout",
          string.pred = " ",
          auto.label = TRUE,
          file = here("Output", "Supplement", "Tab_5.html"))

```

Second set of models: EU and national turnout, integer IV

```{r}
# reg turnout
M30 = lm(turnout ~ EES_GGM_huge_np_i + EES_GGM_huge_aspl + country + year + 
           pola + gallagher, data = turnout)
M31 = lm(turnout ~ EES_GGM_glasso_np_i + EES_GGM_glasso_aspl + country + year + 
           pola + gallagher, data = turnout)
M32 = lm(turnout ~ EES_COR_np_i + EES_COR_aspl + country + year +
           pola + gallagher, data = turnout)

M33 = lm(turnout_nat ~ EES_GGM_huge_np_i + EES_GGM_huge_aspl + country + year +
           pola + gallagher, data = turnout)
M34 = lm(turnout_nat ~ EES_GGM_glasso_np_i + EES_GGM_glasso_aspl + country + year +
           pola + gallagher, data = turnout)
M35 = lm(turnout_nat ~ EES_COR_np_i + EES_COR_aspl + country + year + 
           pola + gallagher, data = turnout)

tab_model(list(M30, M31, M32, M33, M34, M35),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M30 (EU turnout)", "M31 (EU turnout)", 
                        "M32 (EU turnout)", "M33 (National turnout)",
                        "M34 (National turnout)", "M35 (National turnout)"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "OLS fixed effects (country and years) on EU and National turnout",
          string.pred = " ",
          auto.label = TRUE,
          file = here("Output", "Supplement", "Tab_6.html"))

```


## Figure 2 (Article)


```{r}
#Figure_2

# Get the predicted values and confidence intervals using ggeffects
predicted_values <- ggeffects::predict_response(M24, terms = "EES_GGM_huge_np_w",
                                                margin = "marginalmeans") %>%
  as.data.frame()

# Mutate the country_year column in the original data
data_scatt_2 <- turnout %>%
  mutate(
    iso2c = countrycode(substr(country_year, 1, 3), "iso3c", "iso2c"),
    year = substr(country_year, 7, 8),
    country_year_modified = paste(iso2c, year, sep = "_")
  )

# Rename variables in predicted_values to avoid conflicts
predicted_values <- predicted_values %>%
  rename(EES_GGM_huge_np_w = x, predicted_turnout = predicted)

# Plot with the true regression line and SE
scatt2 <- ggplot(data_scatt_2, aes(x = EES_GGM_huge_np_w, y = turnout)) +
  geom_point(size = 1) +
  geom_ribbon(data = predicted_values, aes(x = EES_GGM_huge_np_w, ymin = conf.low, ymax = conf.high), inherit.aes = FALSE, alpha = 0.2, fill = "#69b3a2") +
  geom_line(data = predicted_values, aes(x = EES_GGM_huge_np_w, y = predicted_turnout), inherit.aes = FALSE, color = "pink", size = 1) +
  theme(plot.margin = margin(0, 0, 0, 0, "pt")) +
  theme_ipsum(base_size = 14) +
  labs(x = "Ratio negative positive edges",
       y = "EU turnout") +
  geom_text_repel(data = subset(data_scatt_2, !country_year_modified %in% c("IE_94", "AT_19")),
                  aes(label = country_year_modified), size = 2) +
  geom_label_repel(data = subset(data_scatt_2, country_year_modified %in% c("IE_94", "AT_19")),
                   aes(label = country_year_modified),
                   size = 3,
                   box.padding = 0.3,
                   point.padding = 0.5,
                   label.size = 0.25,
                   fill = 'white',
                   color = 'black')

print(scatt2)

#save
ggsave(here("Output", "Article", "Figure_2.jpg"), scatt2, width = 180, height = 180, units = "mm", dpi = 600)
```

Here is the scatterplot for the national elections

```{r}
#Figure_3

# Get the predicted values and confidence intervals using ggeffects
predicted_values_M27 <- ggpredict(M27, terms = "EES_GGM_huge_np_w",
                                                margin = "marginalmeans") %>%
  as.data.frame()

# Mutate the country_year column in the original data
data_scatt_3 <- turnout %>%
  mutate(
    iso2c = countrycode(substr(country_year, 1, 3), "iso3c", "iso2c"),
    year = substr(country_year, 7, 8),
    country_year_modified = paste(iso2c, year, sep = "_")
  )

# Rename variables in predicted_values to avoid conflicts
predicted_values_M27 <- predicted_values_M27 %>%
  rename(EES_GGM_huge_np_w = x, predicted_turnout_nat = predicted)

# Plot with the true regression line and SE
scatt3 <- ggplot(data_scatt_3, aes(x = EES_GGM_huge_np_w, y = turnout_nat)) +
  geom_point(size = 1) +
  geom_ribbon(data = predicted_values_M27, aes(x = EES_GGM_huge_np_w, ymin = conf.low, ymax = conf.high), inherit.aes = FALSE, alpha = 0.2, fill = "#69b3a2") +
  geom_line(data = predicted_values_M27, aes(x = EES_GGM_huge_np_w, y = predicted_turnout_nat), inherit.aes = FALSE, color = "pink", size = 1) +
  theme(plot.margin = margin(0, 0, 0, 0, "pt")) +
  theme_ipsum(base_size = 14) +
  labs(x = "Ratio negative positive edges",
       y = "National turnout") +
  geom_text_repel(data = subset(data_scatt_3, !country_year_modified %in% c("IE_94", "AT_19")),
                  aes(label = country_year_modified), size = 2) +
  geom_label_repel(data = subset(data_scatt_3, country_year_modified %in% c("IE_94", "AT_19")),
                   aes(label = country_year_modified),
                   size = 3,
                   box.padding = 0.3,
                   point.padding = 0.5,
                   label.size = 0.25,
                   fill = 'white',
                   color = 'black')

print(scatt3)

#save
ggsave(here("Output", "Article", "Figure_2_national.jpg"), scatt3, width = 180, height = 180, units = "mm", dpi = 600)
```

The combined plot

```{r, echo=FALSE}
## Combine the plots using patchwork
#combined_plot_2 <- scatt2 + scatt3
#plot_layout(ncol = 1, heights = c(0, 0, 0), guides = "collect") & 
#theme(plot.margin = margin(0,0,0,0, "cm"))
#
## Print the combined plot
#print(combined_plot_2)
#
###save
##ggsave(here("Output", "Article", "Figure_2.jpg"), combined_plot_2, width = 180, #height = 90, units = "mm", dpi = 600)
```

Figure 3 with pola rather than ratio measure
```{r}
#Figure_3

# Get the predicted values and confidence intervals using ggeffects
predicted_values_M27 <- ggpredict(M27, terms = "pola",
                                                margin = "marginalmeans") %>%
  as.data.frame()

# Mutate the country_year column in the original data
data_scatt_3 <- turnout %>%
  mutate(
    iso2c = countrycode(substr(country_year, 1, 3), "iso3c", "iso2c"),
    year = substr(country_year, 7, 8),
    country_year_modified = paste(iso2c, year, sep = "_")
  )

# Rename variables in predicted_values to avoid conflicts
predicted_values_M27 <- predicted_values_M27 %>%
  rename(pola = x, predicted_turnout_nat = predicted)

# Plot with the true regression line and SE
scatt3 <- ggplot(data_scatt_3, aes(x = pola, y = turnout_nat)) +
  geom_point(size = 1) +
  geom_ribbon(data = predicted_values_M27, aes(x = pola, ymin = conf.low, ymax = conf.high), inherit.aes = FALSE, alpha = 0.2, fill = "#69b3a2") +
  geom_line(data = predicted_values_M27, aes(x = pola, y = predicted_turnout_nat), inherit.aes = FALSE, color = "pink", size = 1) +
  theme(plot.margin = margin(0, 0, 0, 0, "pt")) +
  theme_ipsum(base_size = 14) +
  labs(x = "Political polarization",
       y = "National turnout") +
  geom_text_repel(data = subset(data_scatt_3, !country_year_modified %in% c("IE_94", "AT_19")),
                  aes(label = country_year_modified), size = 2)

print(scatt3)

#save
ggsave(here("Output", "Article", "Figure_3_national_pola.jpg"), scatt3, width = 180, height = 180, units = "mm", dpi = 600)
```

## Figure_3

```{r}
# import network data to show examples
EES_data = read_rds(here("Input", "data", "EES.rds"))

#Network models
irl_94_fit = estimateNetwork(EES_data[["1994"]][["IRL"]], default = "huge", tuning = 0.15)
aut_19_fit = estimateNetwork(EES_data[["2019"]][["AUT"]], default = "huge", tuning = 0.15)

#Network matrices for highlighted cases
irl_94 = irl_94_fit$graph
aut_19 = aut_19_fit$graph

#irl_94
shortnames_irl_94 = c("GP", "DL", "Lab", "PD", "FG", "FF", "SF")
longnames_irl_94 = c("Green Party", "Democratic Left", "Labour Party", "Progressive Democrats", "Fine Gael", 
                     "Fianna Fail", "Sinn Fein")

#irl_94
irl_94_graph<-qgraph(irl_94, 
  layout = "spring", theme = "Borkulo", GLratio = 2,
  labels = shortnames_irl_94, nodeNames = longnames_irl_94,
  label.scale=FALSE, label.cex = 1, borders = F,
  legend.cex = 0.45, legend = TRUE, details = FALSE, vsize=7.0,
 title = "Ireland 1994", color = "#69b3a2",
 filetype="jpg", filename=here("Output", "Article", "Figure_3", "Figure_3_a"))

#aut_19
shortnames_aut_19 = c("ÖVP", "SPÖ", "NEOS", "DG", "FPÖ", "BZÖ")
longnames_aut_19 = c("Austrian People's Party", "Austrian Social Democratic Party", "The New Austria and Liberal Forum", 
                     "The Greens")

aut_19_graph<-qgraph(aut_19, GLratio = 2, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames_aut_19, nodeNames = longnames_aut_19,
  label.scale=FALSE, label.cex = 1, borders = F,
  legend.cex = 0.45, legend = TRUE, details = FALSE, vsize=7.0,
 title = "Austria 2019", color = "#69b3a2",
 filetype="jpg", filename=here("Output", "Article", "Figure_3", "Figure_3_b"))
```

## Fig_7 (Supplement)
A closer inspection of the variable mandatory voting. It was previously scoring 1 for countries with STRICT legislation for mandatory voting. It is now scoring 1 also for countries with WEAK legislation for mandatory voting (this is the coding of the IDEA database). 

Mandatory voting is not so highly correlated with country (biserial r = 0.22), but the association is significant (chisq pval = 0.000). Here is a table between country and mandatory voting. 

```{r, include=FALSE, warning=FALSE}
#country_num = as.numeric(turnout$country)
#mand_num = as.numeric(turnout$mand)
#
#biserial.cor(country_num, mand_num)
#stats::chisq.test(country_num, mand_num)
```

```{r}
#tab_1 = turnout %>% 
#  select(country_year, country, mand)
#
## Print the table 
#kable(tab_1, caption = "Table 1: Country and Mandatory voting") %>%
#  kable_styling(bootstrap_options = "striped",
#                full_width = T)
```

Here a modified scatterplot which indicates mandatory voting is likely to have a significant impact on this relationship. 
The countries with higher turnout are indeed those with the strict legislation on compulsory voting. These are: Belgium, Luxembourg, Greece. 

```{r}
# Plot with colored dots
scatt_mand <- ggplot(data_scatt_2, aes(x = EES_GGM_huge_np_w, y = turnout, color = as.factor(mand))) +
  geom_point(size = 1) +
  geom_smooth(method = lm, color = "pink", fill = "#69b3a2", se = TRUE) +
  theme(plot.margin = margin(0, 0, 0, 0, "pt")) +
  theme_ipsum() +
  labs(x = "Ratio negative positive edges",
       y = "EU turnout",
       color = "Mandatory voting") +  
  geom_text_repel(aes(label = country_year_modified), size = 2)

print(scatt_mand)

#save
ggsave(here("Output", "Supplement", "Fig_7.jpg"), scatt_mand, width = 16, height = 9, dpi = 600)
```



