---
title: "Robustness checks"
author: "Arturo Bertero"
date: "2024-04-15"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library("pacman")
p_load(tidyverse, here, haven, countrycode, vdemdata, psych, lavaan, ltm, patchwork,
       kableExtra, lme4, lmerTest, conflicted, stringr, sjPlot, car, ggplot2)

#conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
```

# Input

```{r}
# import final data
data = read_rds(here("Input", "final_data", "final.rds"))

```


# Processing

Correlation between the measures, before rescaling and centering. Variables are:

**Mean_Constraint**: mean of absolute differences between PTV scores
**PTV_GAP**: max - second max PTV score
**AP**: spread of PTV scores, formula is [here](https://www.sciencedirect.com/science/article/abs/pii/S0261379420300822?via%3Dihub) 
**DIFF_SD**: SD of absolute differences of PTV scores
**PTV_SD**: SD of raw PTV scores
**PTV_M**: mean of PTV scores

```{r}
# Check cors

# Standard Pearson Correlations (ignores multilevel structure)
cor_matrix <- data %>%
  select(Mean_Constraint, PTV_Gap, AP, DIFF_SD, PTV_SD, PTV_M) %>%
  cor(use = "pairwise.complete.obs")

print(cor_matrix)
```
Mean constraint is virtually the same variable as the SD of PTV scores. 
PTV_Gap is mainly similar to AP, but differ a lot with respect to Constraint. 
AP is basically the SD of raw PTV scores (PTV_SD) or the SD of the absolute differences between PTV scores.

Now some basic plot of the mean of these variables at the country-year level:

```{r}
# Aggregate data at the country-year level (taking the mean per country_year)
data_agg <- data %>%
  group_by(country_year) %>%
  summarize(across(c(Mean_Constraint, PTV_Gap, AP, DIFF_SD, PTV_SD, PTV_M), mean, na.rm = TRUE)) %>%
  pivot_longer(cols = -country_year, names_to = "Variable", values_to = "Value")

# Create histograms of country-year aggregated data
p <- ggplot(data_agg, aes(x = Value)) +
  geom_histogram(fill = "gray30", color = "black", bins = 30) +
  facet_wrap(~Variable, scales = "free") +
  theme_minimal() +
  labs(title = "Distributions of Key Variables (Aggregated at Country-Year Level)",
       x = "Mean Value per Country-Year", 
       y = "Count")

# Print the plot
print(p)

```


```{r}
# Check variable types
#str(data)

# Check factors
table(data$vote, useNA = "always")
table(data$vote_choice, useNA = "always")
table(data$sex, useNA = "always")
table(data$partisan, useNA = "always")

# General summary
#summary(data)

```

```{r}
# Function to rescale and center numeric variables within country_year
rescale_and_center <- function(data, var_name) {
  
  if (var_name %in% names(data) && is.numeric(data[[var_name]])) {
    
    # Rescale to 0-1
    data <- data %>%
      mutate(!!sym(var_name) := (get(var_name) - min(get(var_name), na.rm = TRUE)) / 
                                 (max(get(var_name), na.rm = TRUE) - min(get(var_name), na.rm = TRUE)))
    
    # Center within country_year
    data <- data %>%
      group_by(country_year) %>%
      mutate(!!sym(paste0(var_name, "_centered")) := get(var_name) - mean(get(var_name), na.rm = TRUE)) %>%
      ungroup()
    
  } else {
    message(paste("Skipping:", var_name, "- Not a numeric variable"))
  }
  
  return(data)
}

```

```{r}
#Apply the function to all key PTV measures

data = rescale_and_center(data, "Mean_Constraint")
data = rescale_and_center(data, "PTV_Gap")
data = rescale_and_center(data, "AP")
data = rescale_and_center(data, "DIFF_SD")
data = rescale_and_center(data, "PTV_SD")
data = rescale_and_center(data, "PTV_M")

# Apply to individual level numeric controls
data = rescale_and_center(data, "pol_int")
data = rescale_and_center(data, "yb")
data = rescale_and_center(data, "class")

# Apply to country-level numeric controls
data = rescale_and_center(data, "ENEP")
data = rescale_and_center(data, "inflation")

# center year in a different way
data <- data %>%
  mutate(year_centered = year - 1989)
```


## Models


### Baseline
I fit exploratory models where each re-scaled and centered PTV-derived variable
predicts vote/no vote. 

```{r}
# Ensure all models use the same data subset 
data_1 <- data %>%
  select(vote,  country_year, Mean_Constraint_centered, PTV_Gap_centered, AP_centered, DIFF_SD_centered,
         PTV_SD_centered, PTV_M_centered) %>% 
  na.omit()

# Fit a logistic multilevel model with random intercepts
m1 <- glmer(vote ~ Mean_Constraint_centered + (1 | country_year), 
            data = data_1, 
            family = binomial())

m2 <- glmer(vote ~ PTV_Gap_centered + (1 | country_year), 
            data = data_1, 
            family = binomial())

m3 <- glmer(vote ~ AP_centered + (1 | country_year), 
            data = data_1, 
            family = binomial())

m4 <- glmer(vote ~ DIFF_SD_centered + (1 | country_year), 
            data = data_1, 
            family = binomial())

m5 <- glmer(vote ~ PTV_SD_centered + (1 | country_year), 
            data = data_1, 
            family = binomial())

m6 <- glmer(vote ~ PTV_M_centered + (1 | country_year), 
            data = data_1, 
            family = binomial())

#list of models
m_list = list(m1, m2, m3, m4, m5, m6)

# sjPlot
tab_model(m_list, show.re.var = TRUE, 
          show.icc = TRUE, 
          show.aic = TRUE, 
          dv.labels = "Predicting Vote (Multilevel Model)",
          title = "Logistic Multilevel Model Predicting Vote")


```

The highest OR are for Mean constraint and PTV_SD. 

### Individual level controls

```{r}
# Ensure all models use the same data subset 
data_2 <- data %>%
  select(vote,  country_year, Mean_Constraint_centered, PTV_Gap_centered, AP_centered, DIFF_SD_centered,
         PTV_SD_centered, PTV_M_centered, pol_int_centered, partisan, sex, yb_centered, class_centered) %>% 
  na.omit()

# Fit a logistic multilevel model with random intercepts
m1_2 <- glmer(vote ~ Mean_Constraint_centered +
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            + (1 | country_year), 
            data = data_2, 
            family = binomial())

m2_2 <- glmer(vote ~ PTV_Gap_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            + (1 | country_year), 
            data = data_2, 
            family = binomial())

m3_2 <- glmer(vote ~ AP_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            + (1 | country_year), 
            data = data_2, 
            family = binomial())

m4_2 <- glmer(vote ~ DIFF_SD_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            + (1 | country_year), 
            data = data_2, 
            family = binomial())

m5_2 <- glmer(vote ~ PTV_SD_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            + (1 | country_year), 
            data = data_2, 
            family = binomial())

m6_2 <- glmer(vote ~ PTV_M_centered + 
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            + (1 | country_year), 
            data = data_2, 
            family = binomial())

#list of models
m2_list = list(m1_2, m2_2, m3_2, m4_2, m5_2, m6_2)

# sjPlot
tab_model(m2_list, show.re.var = TRUE, 
          show.icc = TRUE, 
          show.aic = TRUE, 
          dv.labels = "Predicting Vote (Multilevel Model)",
          title = "Logistic Multilevel Model Predicting Vote, with individual level controls")
```

All models converged without warnings. Note that I rescaled and centered all variables 
but the factors (partisan and sex, both dummies).

The highest OR remain those of Mean constraint and PTV_SD.

### Country level controls

```{r}
# Ensure all models use the same data subset 
data_3 <- data %>%
  select(vote, country_year, 
         Mean_Constraint_centered, PTV_Gap_centered, AP_centered, DIFF_SD_centered,
         PTV_SD_centered, PTV_M_centered, 
         pol_int_centered, partisan, sex, yb_centered, class_centered,  # Individual-level
         ENEP_centered, inflation_centered, mand) %>%  # Country-level
  na.omit()

# Fit a logistic multilevel model with random intercepts (Baseline with Constraint)
m1_3 <- glmer(vote ~ Mean_Constraint_centered +
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# PTV Gap Model
m2_3 <- glmer(vote ~ PTV_Gap_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# Affective Polarization (AP) Model
m3_3 <- glmer(vote ~ AP_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# DIFF_SD Model (Variance in Differences)
m4_3 <- glmer(vote ~ DIFF_SD_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# PTV_SD Model (Variance in PTVs)
m5_3 <- glmer(vote ~ PTV_SD_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# PTV_M Model (Mean PTV Score)
m6_3 <- glmer(vote ~ PTV_M_centered + 
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# List of models
m3_list = list(m1_3, m2_3, m3_3, m4_3, m5_3, m6_3)

# sjPlot
tab_model(m3_list, show.re.var = TRUE, 
          show.icc = TRUE, 
          show.aic = TRUE, 
          dv.labels = "Predicting Vote (Multilevel Model, Full Controls)",
          title = "Logistic Multilevel Model Predicting Vote, with individual and country-level controls")

```

Again, no warnings! 

Main result is that the OR of Mean constraint and PTV_SD remain significant and very high. 
These OR are comparable to those of country-level variables (e.g.: mand [mandatory voting]) and
individual level ones (pol interest)

### Comparison between measures
I now test if Constraint or PTV_SD are better than AP

```{r}
# Compare full models using AIC/BIC
model_comparison <- data.frame(
  Model = c("Full Model (Mean Constraint)", 
            "Full Model (Affective Polarization)", 
            "Full Model (PTV_SD)"),
  AIC = c(AIC(m1_3), AIC(m3_3), AIC(m5_3)),
  BIC = c(BIC(m1_3), BIC(m3_3), BIC(m5_3)),
  LogLikelihood = c(logLik(m1_3), logLik(m3_3), logLik(m5_3))
)

print(model_comparison)
```

Best is PTV_SD, then AP, then Constraint. Now the formal test:

```{r}
# Likelihood Ratio Tests
anova(m3_3, m1_3, test = "Chisq")  # Mean Constraint vs. Affective Polarization
anova(m3_3, m5_3, test = "Chisq")  # PTV_SD vs. Affective Polarization
```
Results are confirmed. We should work with the SD of PTV scores directly I guess. 
But the gap between AP and constraint is very tiny.


### Interactions

#### with PTV_M
I specify an individual level interaction between mean constraint and PTV_M. This would
tell us if the role of constraint varies across mean levels of PTV scores. I do the same interaction
also for the other best predictors we have found: PTV_SD. 

```{r}
# Mean Constraint Model with Interaction
m1_3_interaction <- glmer(vote ~ Mean_Constraint_centered * PTV_M_centered +  # Interaction term
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# PTV_SD Model with Interaction
m5_3_interaction <- glmer(vote ~ PTV_SD_centered * PTV_M_centered +  # Interaction term
            pol_int_centered + partisan + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +                        # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# List of interaction models
m3_list_interaction <- list(m1_3_interaction, m5_3_interaction)

# sjPlot: Displaying the results in a neat table
tab_model(m3_list_interaction, show.re.var = TRUE, 
          show.icc = TRUE, 
          show.aic = TRUE, 
          dv.labels = "Predicting Vote (Multilevel Model, Interaction Included)",
          title = "Logistic Multilevel Model Predicting Vote with Interaction (Constraint × PTV Mean)")

```

The effect of constraint on voting is reduced when PTV Mean is high. So 
when individuals like fewer parties (lower PTV_M), constraint plays a stronger role
in motivating turnout.

In the same vein, the effect of PTV_SD (variance in PTV scores) on voting is weaker
for those with higher PTV_M.

#### with Partisanship
I fit the same models, but interacting with Partisanship (dummy). I think this might
be cleaner cause the measure are more independent (cause partisanship is not built from
PTV).

```{r}
# Mean Constraint Model with Interaction (Mean Constraint × Partisanship)
m1_4_interaction <- glmer(vote ~ Mean_Constraint_centered * partisan +  # Interaction term
            pol_int_centered + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +              # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# PTV_SD Model with Interaction (PTV_SD × Partisanship)
m5_4_interaction <- glmer(vote ~ PTV_SD_centered * partisan +  # Interaction term
            pol_int_centered + sex + yb_centered + class_centered +  # Individual-level
            ENEP_centered + inflation_centered + mand +              # Country-level
            (1 | country_year), 
            data = data_3, 
            family = binomial())

# List of interaction models
m4_list_interaction <- list(m1_4_interaction, m5_4_interaction)

# sjPlot: Displaying the results in a neat table
tab_model(m4_list_interaction, show.re.var = TRUE, 
          show.icc = TRUE, 
          show.aic = TRUE, 
          dv.labels = "Predicting Vote (Multilevel Model, Interaction Included)",
          title = "Logistic Multilevel Model Predicting Vote with Interaction (Constraint × Partisanship)")

```

The effect of Constraint on voting is weaker for partisans. So higher constraint boosts
turnout more among non-partisans.
Same thing for the interaction between PTV_SD and partisanship. Greater differentiation
in party evaluations increases turnout more for non-partisans.


#### With time

```{r}
# interaction between ap and year
m7_3 <- glmer(vote ~ AP_centered * year_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  
            ENEP_centered + inflation_centered + mand +                        
            (1 | country_year), 
            data = data, 
            family = binomial())

```

```{r}
# interaction SD and year
m8_3 <- glmer(vote ~ PTV_SD_centered * year_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  
            ENEP_centered + inflation_centered + mand +                        
            (1 | country_year), 
            data = data, 
            family = binomial())

```

```{r}
# interaction AP and year
m9_3 <- glmer(vote ~ AP_centered * year_centered + PTV_SD_centered * year_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  
            ENEP_centered + inflation_centered + mand +                        
            (1 | country_year), 
            data = data, 
            family = binomial())


```


```{r}
# interactions together
m9_3 <- glmer(vote ~ AP_centered * year_centered + PTV_SD_centered * year_centered +  
            pol_int_centered + partisan + sex + yb_centered + class_centered +  
            ENEP_centered + inflation_centered + mand +                        
            (1 | country_year), 
            data = data, 
            family = binomial())

summary(m9_3)

```



















